\bf\mftitle

### 2011-01-25 doc/jInfer/base/base.tex
Documentation: Base and BasicIGG modules.

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & vektor \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & none \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.base.automaton \newline
cz.cuni.mff.ksi.jinfer.base.interfaces \newline
cz.cuni.mff.ksi.jinfer.base.interfaces.inference \newline
cz.cuni.mff.ksi.jinfer.base.interfaces.nodes \newline
cz.cuni.mff.ksi.jinfer.base.objects \newline
cz.cuni.mff.ksi.jinfer.base.objects.nodes \newline
cz.cuni.mff.ksi.jinfer.base.regexp \newline
cz.cuni.mff.ksi.jinfer.base.utils \newline
org.apache.log4j.* \\ \hline
\end{tabular}

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Matej Vitásek \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & none \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.base.automaton \\ 
& cz.cuni.mff.ksi.jinfer.base.interfaces \\ 
& cz.cuni.mff.ksi.jinfer.base.interfaces.inference \\ 
& cz.cuni.mff.ksi.jinfer.base.interfaces.nodes \\
& cz.cuni.mff.ksi.jinfer.base.objects \\ 
& cz.cuni.mff.ksi.jinfer.base.objects.nodes \\ 
& cz.cuni.mff.ksi.jinfer.base.regexp \\ 
& cz.cuni.mff.ksi.jinfer.base.utils \\
& org.apache.log4j.* \\ \hline
\end{tabular}
